Attack-Tolerant Networks: A Structural, Multipath Approach

### 2016-08-07 wsdm-2017/source/paper.tex
Revise conclusion.

We have developed a partial trust model which enables a formal analysis
of the effect of decentralized network structure on fault tolerance properties.
We have also proposed a general technique for achieving and evaluating adversarial
fault tolerance in a structured network with partial trust.
We found that the probability of an adversary causing an undetectable error
decreases exponentially as the number of redundant paths between the
neighborhoods of the sender and receiver grows.
This property puts attackers at a disadvantage, creating a stabilizing
asymmetry which disincentivizes attack.
We also presented a specific implementation of the multipath fault tolerance
technique on a wraparound butterfly network topology and proved that the
number of redundant paths grows exponentially with number of network hops
that can be trusted.
Our results are directly applicable to architectures in which the link structure
can be imposed by the architect,
and provide a formalism that can be used more generally to evaluate the role
of network structure and redundancy on the fault tolerance of decentralized
networks.

>>>>

We have developed a partial trust model which enables a formal analysis
of the effect of network structure and trust transitivity on
redundancy.
We have also proposed a multipath fault tolerance scheme
for using this redundancy to achieve adversarial
fault tolerance.
Under this scheme, the probability of an adversary causing an undetectable error
decreases exponentially with the network's effective redundancy.
Furthermore, a small increase in the number of messages sent can compensate
for a large increase in the number of messages compromised by an adversary.
This stabilizing asymetry puts attackers at a disadvantage,
disincentivizing attack.
We also presented a novel multipath routing algorithm allowing multipath fault
tolerance to be used on the butterfly topology,
and proved that the effective redundancy of the butterfly network increases
exponentially with the trust radius.
These results are directly applicable to architectures in which the link
structure can be imposed by the architect,
and more generally, provide a formalism that can be used more to evaluate
the role of network structure, trust transitivity, and effective redundancy
on adversarial fault tolerance.
